Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-08 longSC.tex
same for parameterization instead of parametrization

Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.  A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone are unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of heavy-ion system evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_4}.
For SC(3,2), the calculation with the default AMPT settings is closet to the data, but none of the AMPT configurations can describe the data fully. 
The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possibe to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all the centrality ranges.

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models. The difference of the model calculation between two parametrizations is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%. However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities. 
While the difference of the model calculations between two parametrizations in most of the centrality ranges is rather small, the clear separation between two parametrizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

>>>>

Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.  A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone are unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of heavy-ion system evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_4}.
For SC(3,2), the calculation with the default AMPT settings is closet to the data, but none of the AMPT configurations can describe the data fully. 
The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all the centrality ranges.

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two parameterizations is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%. However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities. 
While the difference of the model calculations between two parameterizations in most of the centrality ranges is rather small, the clear separation between two parameterizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
